%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Long Professional Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.latextemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above

\newsectionwidth{0pt} % Stops section indenting

\begin{document}

%----------------------------------------------------------------------------------------
%	YOUR NAME AND ADDRESS(ES) SECTION
%----------------------------------------------------------------------------------------
{\large \textbf{Curriculum Vitae}}\\

\name{Levi King\\ \\} % Your name at the top

% If you don't want one of the addresses, simply remove all the text in the first or second \address{} bracket

\address{Mountain View, CA \\ leviking@iu.edu} % Your address 1

\address{} % Your address 2

%----------------------------------------------------------------------------------------

\begin{resume}

%----------------------------------------------------------------------------------------
%	OBJECTIVE SECTION
%----------------------------------------------------------------------------------------

%\section{\centerline{OBJECTIVE}}
%
%\vspace{8pt} % Gap between title and text
%
%A position in Personnel Administration utilizing skills in recruiting, training and compensation.\\ 

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{EDUCATION}} 

\vspace{9pt} % Gap between title and text

{\sl \textbf{Indiana University}, Bloomington, IN} \hfill expected August 2021 \\
PhD in Linguistics; minor in Second Language Studies; GPA: 3.9 \\ 
Advisors: Markus Dickinson, Sandra Kuebler, David Stringer (Dept. of Linguistics), Sunyoung Shin (Dept. of Second Language Studies) \\
Dissertation: Semantic Analysis of Image-Based Learner Sentences \\
Defense Date: August 6, 2021 \\

{\sl \textbf{Indiana University}, Bloomington, IN} \hfill May 2011 \\
MA in Linguistics/TESOL, GPA: 3.9 \\ 
Advisors: Markus Dickinson (Dept. of Linguistics), Kathleen Bardovi-Harlig (Dept. of Second Language Studies) \\

{\sl \textbf{Ball State University}, Muncie, IN} \hfill August 2004 \\ 
BA in English, GPA: 3.8 \\
Advisor: Barbara Stedman (Dept. of English) \\

%----------------------------------------------------------------------------------------
 
\vspace{0.2in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
%	PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{PROFESSIONAL EXPERIENCE}} 

\vspace{9pt} % Gap between title and text

{\sl \textbf{Adecco, onsite at Google}, Mountain View, CA} \hfill September 2018 -- June 2020 \\
\textbf{Speech Data Ops Language Engineer}\\
Migrated text-to-speech pipelines from obsolete pronunciation systems to a unified system for 70+ languages and launched 10+ new languages. Wrote automation tools, updated unit tests, built, compared and debugged voices in collaboration with linguists and engineers.

{\sl \textbf{IU Dept. of Second Language Studies}, Bloomington, IN} \hfill 2008--2011, 2016--2017 \\
\textbf{ESL Instructor \& Testing Assistant} \\
Administered placement exams and interviews of incoming international students and teaching assistant candidates; conducted scoring and data analysis. Taught English courses to adult learners with various language backgrounds and proficiency levels in the Intensive English Program. Taught advanced literacy in the English Language Improvement Program.

{\sl \textbf{Linguist List}, Bloomington, IN} \hfill Summer 2015 \\
\textbf{Volunteer Research Assistant} \\
Worked 20 hours per week with a team to develop a Yiddish automatic speech recognition system. Tasks involved automating phonetic transcription from annotations and developing acoustic models via forced alignment.

{\sl \textbf{IU Department of Linguistics}, Bloomington, IN} \hfill May 2012 -- December 2014 \\
\textbf{Research Assistant / Webmaster} \\
Produced annual department newsletters. Maintained previous department website; co-developed new department website. Produced flyers and websites for workshops and special events.

\clearpage

{\sl \textbf{IU Department of Linguistics}, Bloomington, IN} \hfill May 2011 -- May 2012 \\
\textbf{Corpus Annotator} \\
Edited automatic annotation and performed manual annotation for the POS tagging, constituency parsing and dependency parsing of a spoken dialog corpus (Cooperative Remote Search Task (CReST) Corpus) for an Office of Naval Research project.

{\sl \textbf{Fulbright Foundation}} \hfill June 2006 -- June 2007 \\
\textbf{Fulbright English Teaching Assistant} \\
Taught first through sixth grade students at two elementary schools in rural Taiwan. Developed educational DVDs and materials for local schools. Coached students for English competitions. Hosted workshops for local English teachers.
%----------------------------------------------------------------------------------------

\vspace{0.2in} % Some whitespace between sections

\section{\centerline{PUBLICATIONS}} 
\vspace{9pt} % Some whitespace between sections

Levi King and Markus Dickinson. 2018. Annotating Picture Description Task Responses for Content Analysis. In \textit{Proceedings of the 13th Workshop on Innovative Use of NLP for Building Educational Applications (BEA13)}. New Orleans, LA. pp. 101--109.
%%------------------------------------------------
\vspace{9pt}

Levi King and Markus Dickinson. 2016. Shallow Semantic Reasoning from an Incomplete Gold Standard for Learner Language. In \textit{Proceedings of the 11th Workshop on Innovative Use of NLP for Building Educational Applications (BEA11)}. San Diego, CA. pp. 112--121.
%%------------------------------------------------
\vspace{9pt}

Levi King and Markus Dickinson. 2014. Leveraging Known Semantics for Spelling Correction. In \textit{Proceedings of the Third Workshop on NLP for Computer-Assisted Language Learning (NLP4CALL)}. Uppsala, Sweden. pp. 43--58.
%%------------------------------------------------
\vspace{9pt}

Levi King, Eric Baucom, Timur Gilmanov, Sandra Kuebler, Daniel Whyatt, Wolfgang Maier, and Paul Rodrigues. 2014. The IUCL+ System: Word-Level Language Identification via Extended Markov Models. In \textit{Proceedings of the First Workshop on Computational Approaches to Code-Switching}. Doha, Qatar. pp. 102--6.
%------------------------------------------------
\vspace{9pt}

Alex Rudnick, Levi King, Can Liu, Markus Dickinson, Sandra Kuebler. 2014. IUCL: Combining Information Sources for SemEval Task 5. In \textit{Proceedings of the 8th International Workshop on Semantic Evaluation (SemEval 2014)}. Dublin, Ireland. pp. 356-60.
%------------------------------------------------
\vspace{9pt}

Eric Baucom, Levi King and Sandra Kuebler. 2013. Domain Adaptation for Parsing. In \textit{Proceedings of the 9th Conference on Recent Advances in Natural Language Processing (RANLP-13)}. Hissar, Bulgaria. pp. 56--64.
%------------------------------------------------
\vspace{9pt}

Levi King and Markus Dickinson. 2013. Shallow Semantic Analysis of Interactive Learner Sentences. In \textit{Proceedings of the Eighth Workshop on Innovative Use of NLP for Building Educational Applications (BEA8)}. Atlanta, GA. pp. 11--21
%------------------------------------------------
\vspace{9pt}


Levi King, Sandra Kuebler and Wallace Hooper. 2013. Word-level Language Identification in ``The Chymistry of Isaac Newton.'' In \textit{Proceedings of the 2013 Digital Humanities Conference}. Lincoln, NE. pp. 258--61.
%%------------------------------------------------

\vspace{0.2in} % Some whitespace between sections

\section{\centerline{PRESENTATIONS}} 
\vspace{9pt}

Levi King. Politeness and Proficiency of English Language Learners Online. Teachers of English to Speakers of Other Languages annual conference (TESOL). Philadelphia, PA. March 31, 2012.

%%------------------------------------------------
\vspace{9pt}

Levi King. Reinforcing Academic Reading Skills Through Mystery Stories. Indiana Teachers of English to Speakers of Other Languages annual conference (INTESOL). Indianapolis, IN. November 19, 2011.

\vspace{0.2in} % Some whitespace between sections

\section{\centerline{SERVICE}} 
\vspace{9pt}

Peer Reviewer: Indiana TESOL Conference, 2011-2012; Extrinsic Parse Improvement (EPI) 2013; Building Educational Applications (BEA) Workshop, 2014-2019; Digital Humanities Conference, 2014; SemEval Workshop, 2014-2015.

Volunteer Rater: North American Computational Linguistics Olympiad, 2016, 2018.

%%------------------------------------------------


%%----------------------------------------------------------------------------------------
%%	COMPUTER SKILLS SECTION
%%----------------------------------------------------------------------------------------
%
\vspace{0.2in} % Some whitespace between sections

\section{\centerline{COMPUTER SKILLS}}

\vspace{9pt}

Proficient/Experienced: Python; Excel; Natural Language Toolkit (NLTK); TnT POS Tagger; Aspell \& Enchant spelling correction modules; SENNA semantic role labeler; CMU Statistical Language Modeling (SLM) Toolkit; LATEX; Bash; Berkeley, Stanford, MST, MATE, Malt, LoPar \& DeSR syntactic parsers; Stanford CoreNLP/Stanza
\vspace{9pt}

Moderate Experience: HTML; Adobe Dreamweaver, Illustrator, InDesign, Photoshop \& Premiere; Final Cut Pro X; ELAN; TigerSearch; BERT; SBERT; Word2Vec; NumPy; spaCy; GATE; WordNet; C++; Java; PHP; Perl; WordPress; WEKA; Scikit-learn; KenLM Language Modeling Toolkit; TensorFlow

\vspace{0.2in} % Some whitespace between sections

%----------------------------------------------------------------------------------------
%	MEMBERSHIPS SECTION
%----------------------------------------------------------------------------------------

\section{\centerline{LANGUAGES}} 

\vspace{9pt}

English (native), Spanish (intermediate), Mandarin Chinese (low intermediate)
%----------------------------------------------------------------------------------------
%
%\vspace{0.2in} % Some whitespace between sections
%
%%----------------------------------------------------------------------------------------
%%	HONORS SECTION
%%----------------------------------------------------------------------------------------
%
%\section{\centerline{HONORS}} 
%
%\vspace{-5pt} % Reduce space between section title and contents
%
%\begin{center}
%Full tuition assistantship, Rensselaer Polytechnic Institute \\
%PSI CHI National Honor Society \\
%PHI THETA KAPPA National Honor Society 
%\end{center}
%
%%----------------------------------------------------------------------------------------
%
%\vspace{0.2in} % Some whitespace between sections
%
%%----------------------------------------------------------------------------------------
%%	INTERESTS SECTION
%%----------------------------------------------------------------------------------------
%
%\section{\centerline{INTERESTS}} 
%
%\vspace{-5pt} % Reduce space between section title and contents
%
%\begin{center}
%Classical piano, jazz, bodybuilding/aerobic exercise, cooking, dancing
%\end{center} 
%
%%----------------------------------------------------------------------------------------
%
\end{resume} 
\end{document}