\begin{centering}
\textbf{ACKNOWLEDGEMENTS}\\
\vspace{\baselineskip}
\end{centering}

I would like to thank Markus Dickinson, my main advisor, for his countless hours of help and guidance throughout this dissertation. None of this would have happened without your patience and mentorship. You have been exceedingly generous in sharing both your time and your expertise in matters of linguistics, natural language processing, annotation, learner language, and intelligent computer assisted language learning, not to mention rock music, comedy, and life in general. Thank you for all your efforts in seeing this work through with me. Working with you has been a pleasure and a blessing for which I will be forever grateful.

I would also like to thank the members of my dissertation committee for their invaluable efforts: David Stringer for his expert feedback on matters of second language acquisition and general linguistics; Sunyoung Shin for his excellent input on matters of statistics and language testing; and especially Sandra Kuebler for her consistent expertise, guidance, and generous feedback on matters of natural language processing, dependency grammars, and research design throughout this dissertation and my graduate coursework. Thank you all.

I am also deeply indebted to other professors, colleagues, and friends for all their support in matters personal and academic over the last many years. These people are too many to mention, but I would like to thank in particular the numerous faculty, staff, and friends from the Department of Linguistics and the Department of Second Language Studies at Indiana University Bloomington who kept me on the right path. I would also like to thank all my friends in the Bloomington pottery community for keeping me ``centered'' and offering a much-needed sanctuary from the struggles of academia. I am also very grateful to the members of the Bloomington trivia community, particularly my dear comrades on Team \textit{Sparkle Motion} (aka \textit{Seabass and the Fellas} aka \textit{Hot Ham Water}...) for their enduring friendship; thank you. 

Finally, I would like to thank my family for their moral support through what has been the most challenging enterprise of my life. I am grateful to numerous extended family members, but especially my brothers, Colby and Shaun. Thank you. And most of all, to my mother, Marilyn, thank you dearly. From emotional support to last-minute, late-night proofreading, you were always ready to offer whatever I needed.  Without you and your faith in me, I never would have completed this dissertation.