\chapter{Introduction and Background}

A way out west there was a fella, 
fella I want to tell you about, fella 
by the name of Jeff Lebowski. At 
least, that was the handle his lovin' 
parents gave him, but he never had 
much use for it himself. This 
Lebowski, he called himself the Dude. 
Now, Dude, that's a name no one would 
self-apply where I come from. But 
then, there was a lot about the Dude 
that didn't make a whole lot of sense 
to me. And a lot about where he 
lived, like- wise. But then again, 
maybe that's why I found the place 
s'durned innarestin'...

They call Los Angeles the City of 
Angels. I didn't find it to be that 
exactly, but I'll allow as there are 
some nice folks there. 'Course, I 
can't say I seen London, and I never 
been to France, and I ain't never 
seen no queen in her damn undies as 
the fella says. But I'll tell you 
what, after seeing Los Angeles and 
thisahere story I'm about to unfold--
wal, I guess I seen somethin' ever' 
bit as stupefyin' as ya'd see in any 
a those other places, and in English 
too, so I can die with a smile on my 
face without feelin' like the good 
Lord gypped me.

Now this story I'm about to unfold 
took place back in the early nineties--
just about the time of our conflict 
with Sad'm and the Eye-rackies. I 
only mention it 'cause some- times 
there's a man--I won't say a hee-ro, 
'cause what's a hee-ro?--but sometimes 
there's a man.

And I'm talkin' about the Dude here-- 
sometimes there's a man who, wal, 
he's the man for his time'n place, 
he fits right in there--and that's 
the Dude, in Los Angeles.

...and even if he's a lazy man, and 
the Dude was certainly that--quite 
possibly the laziest in Los Angeles 
County..which would place him high in the 
runnin' for laziest worldwide--but 
sometimes there's a man. . . sometimes 
there's a man.

Wal, I lost m'train of thought here. 
But--aw hell, I done innerduced him 
enough.
